Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-04-30 paper/main.tex
Makefile & manuscript work with newcommand tex-files
add table for AO events

\begin{document}
%\input{descr-stats-ao-events.tex}
%\input{descr-stats-av-events.tex}

@@

A preliminary annotation by one person according to the rules [entweder im laufenden Text oder in einer [eigenständigen] Tabelle]. Minor corrections due to incorrectly applied rules were by the author.

@@

\subsubsection{first-level}
\paragraph{Regressors}
We used an annotation of movie cuts and depicted locations \citep{haeusler2016cutanno} and an annotation of speech \citep{haeusler2020speechanno} to create the FSL event files resp. regressors.
First, both annotations were split via \href{"https://github.com/chrhaeusler/studyforrest-data-annotations/blob/master/code/researchcut2segments.py"}{python script} into eight parts corresponding to the eight segments used as stimuli during fMRI scanning.
\todo[inline]{wenn ich folgend den "null regressor" nehme, darf ich den ganzen Run, glaube ich, in der 2nd level Analyse gar nicht benutzen??}
For the AO stimulus, we used the narrator's ``descriptive nouns'' (cf. table \ref{tab:descr-nouns}.
We created 11 regressors from the XY (selected?) original categories by joining / merging some categories (female, females, fname; male, males, mname; face, head) into one regressor (sex\_f; sex\_m; fahead).

\todo[inline]{cross reference to fig:reg-corr}

\begin{table*}[t]
    \caption{Overview of the events to build the 18 regressors for analysis of the AO stimulus. The first column contains the number of the regressor in the design file of FSL \citep{smith2004fsl}.
''fg\_ad\_lrdiff (left-right volume difference) and ``fg\_ad\_rms'' (root mean square loudness) represent low-level auditory nuissance regressors comprising one event for every movie frame (40ms).}
\label{tab:regressors}
\footnotesize
\begin{tabular}{lp{3.5cm}lllllllll}
\toprule
\textbf{label} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
body & XY & rBodyAll & rBodyI & rBodyII & rBodyIII & rBodyIV & rBodyV & rBodyVI & rBodyVII & rBodyVIII \tabularnewline
fg\_ad\_lrdiff & left-right volume difference & rFgadlrdiffAll & rFgadlrdiffI & rFgadlrdiffII & rFgadlrdiffIII & rFgadlrdiffIV & rFgadlrdiffV & rFgadlrdiffVI & rFgadlrdiffVII & rFgadlrdiffVIII \tabularnewline
fg\_ad\_rms & root mean square & rFgadrmsAll & rFgadrmsI & rFgadrmsII & rFgadrmsIII & rFgadrmsIV & rFgadrmsV & rFgadrmsVI & rFgadrmsVII & rFgadrmsVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

% over length of each noun
The regressors were modeled as boxcar functions at the end of each noun with a duration of 200 ms.
If a segment did not contain a single event for a specific regressor, a null regressor was chosen for that segment.
Five regressors related to the cinematographic cuts (s. below) were added to built contrasts of cross-modal negative control.
Two regressors reflecting auditory (low-level) features (left-right loudness volume / amplitude??? difference; root mean squared amplitude) aligned to the frame rate of (40\,ms) were modeled to reduce nuisance effects.
An overview and short explanation of the 11 regressors and 5 + 2 additional nuisance regressors can be found in Table xy.
% entgegen der Masterarbeit kommen hier für den Film keine Abbildungen zur Verdeutlichung, weniger Text; no cut erkläre ich nicht lang & breit
% die regressoren settinge_new & setting_old aus dem Hörspiel habe ich meiner meinung nach unnötigerweise im Film mit-modelliert; lasse mich da aber auch umstimmen

@@

\begin{table*}
\caption{Regressors used in the analysis of the audio-description. \todo[inline]{make clear which stimulus each annotation is based on, and make clear(er) what defined an event. This could be a big table, because good defintions are important for judging the results}}
\begin{tabular}{lll}
\toprule
\textbf{name} & \textbf{count} & \textbf{description} \\
\midrule
body & 66 & trunk of the body or overlaid clothes \\
bpart & 69 & limbs and trousers \\
facehead & 83 & face(parts) or head(parts) \\
furniture & 50 & big inventory of rooms (insides/outsides) \\
geo & 125 & immobile landmarks \\
geo-room & 105 & elements defining a locale's spatial layout \\
setting\_new & 86 & first-time mentioned setting \\
setting\_old & 37 & recurring setting \\
object & 284 & inanimate entities with firm boundaries \\
sex\_f & 108 & female person(s), name \\
sex\_m & 403 & male person(s), name \\
vse\_new & 96 & control for movie cuts; s. table y \\
vse\_old & 90 & control for movie cuts; s. table y \\
vloc\_change & 89 & control for movie cuts; s. table y \\
vpe\_new & 386 & control for movie cuts; s. table y \\
vpe\_old & 208 & control for movie cuts; s. table y \\
fg\_ad\_lrdiff & xx &  left-right volume difference \\
fg\_ad\_rms & xx & root mean square amplitude \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}
\caption{Regressors used in the analysis of the movie.}
\begin{tabular}{lll}
\toprule
\textbf{name} & \textbf{count} & \textbf{description} \\
\midrule
vse\_new & 96 & change of the camera position to a setting not depicted before \\
vse\_old & 90 & change of the camera position to a recurring setting \\
vloc\_change & 89 & change of the camera position to another locale within the same setting \\
vpe\_new & 386 & change of the camera position within a locale not depicted before \\
vpe\_old & 208 & change of the camera position within a recurring locale \\
no\_cut & 148 & a continuous frame from the same camera position \\
se\_new & 148 & audio-description's narrator; s. table x; KANN RAUS? \\
se\_old & 148 & audio-description's narrator; s. table x; KANN RAUS? \\
fg\_av\_ger\_lr & xx & left right +++???+++ in movie frame  \\
fg\_av\_ger\_lrdiff & xx & left-right volume difference \\
fg\_av\_ger\_pd & xx & perceptual differences of consecutive frames \\
fg\_av\_ger\_rms & xx & root mean square amplitude \\
fg\_av\_ger\_ud & xx & +++up down???+++ \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{document}
\input{descr-stats-ao-events.tex}
\input{descr-stats-av-events.tex}

@@

A preliminary annotation was performed by one person according to the rules (see Table XYZ).
Minor corrections due to incorrectly applied rules were by the author.

@@

\subsubsection{first-level}
\paragraph{Regressors}
\todo[inline]{cross reference to fig:reg-corr}
We used an annotation of movie cuts and depicted locations \citep{haeusler2016cutanno}, and an annotation of speech \citep{haeusler2020speechanno} to create event files for FSL.
% https://github.com/psychoinformatics-de/studyforrest-data-annotations/blob/master/code/researchcut2segments.py}
First, both annotations were split into eight parts corresponding to the eight segments used as stimuli during fMRI scanning.
\todo[inline]{wenn ich folgend den "null regressor" nehme, darf ich den ganzen Run, glaube ich, in der 2nd level Analyse gar nicht benutzen??}
For the AO stimulus, we used the narrator's ``descriptive nouns'' (see Table \ref{tab:descr-nouns}.

\todo[inline]{some categories were pooled, because\dots}

XY from the XY original categories were selected [+++why?+++], and some were pooled  original categories by joining / merging some categories resulting in 11 new categories.

\todo[inline]{make clear which stimulus each annotation is based on, and make clear(er) what defined an event. This could be a big table, because good defintions are important for judging the results}
    \caption{Overview of events to build the 18 regressors for the analysis of the audio-only (AO) stimulus. Some of the original categories (female, females, fname; male, males, mname; face, head; see Table \ref{tab:descr-nouns}) were pooled into new categories (sex\_f; sex\_m; fahead)
\texttt{fg\_ad\_lrdiff} (left-right volume difference) and \texttt{fg\_ad\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).}
\label{tab:ao-events}
\footnotesize
\begin{tabular}{lp{3.5cm}lllllllll}
\textbf{label} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
body & descr & \aoBodyAll & \aoBodyI & \aoBodyII & \aoBodyIII & \aoBodyIV & \aoBodyV & \aoBodyVI & \aoBodyVII & \aoBodyVIII \tabularnewline
bpart & descr & \aoBpartAll & \aoBpartI & \aoBpartII & \aoBpartIII & \aoBpartIV & \aoBpartV & \aoBpartVI & \aoBpartVII & \aoBpartVIII \tabularnewline
fahead & descr & \aoFaheadAll & \aoFaheadI & \aoFaheadII & \aoFaheadIII & \aoFaheadIV & \aoFaheadV & \aoFaheadVI & \aoFaheadVII & \aoFaheadVIII \tabularnewline
furn & descr & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII \tabularnewline
geo & descr & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII & \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII \tabularnewline
groom & descr & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII \tabularnewline
object & descr & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII \tabularnewline
se\_new & descr & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII \tabularnewline
se\_old & descr & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII \tabularnewline
sex\_f & descr & \aoSexfAll & \aoSexfI & \aoSexfII & \aoSexfIII & \aoSexfIV & \aoSexfV & \aoSexfVI & \aoSexfVII & \aoSexfVIII \tabularnewline
sex\_m & descr & \aoSexmAll & \aoSexmI & \aoSexmII & \aoSexmIII & \aoSexmIV & \aoSexmV & \aoSexmVI & \aoSexmVII & \aoSexmVIII \tabularnewline
sex\_u & descr & \aoSexuAll & \aoSexuI & \aoSexuII & \aoSexuIII & \aoSexuIV & \aoSexuV & \aoSexuVI & \aoSexuVII & \aoSexuVIII \tabularnewline
% vlo_ch has no events in segment 5. So indices are shifted
vlo\_ch & descr & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII \tabularnewline
vno\_cut & descr & \aoVnocutAll & \aoVnocutI & \aoVnocutII & \aoVnocutIII & \aoVnocutIV & \aoVnocutV & \aoVnocutVI & \aoVnocutVII & \aoVnocutVIII \tabularnewline
vpe\_new & descr & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII \tabularnewline
% vpe_old has no events in 3. So the indices are shifted
vpe\_old & descr & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII \tabularnewline
vse\_new & descr & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII \tabularnewline
vse\_old & descr & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII \tabularnewline
fg\_ad\_lrdiff & left-right volume difference & \aoFgadlrdiffAll & \aoFgadlrdiffI & \aoFgadlrdiffII & \aoFgadlrdiffIII & \aoFgadlrdiffIV & \aoFgadlrdiffV & \aoFgadlrdiffVI & \aoFgadlrdiffVII & \aoFgadlrdiffVIII \tabularnewline
fg\_ad\_rms & root mean square & \aoFgadrmsAll & \aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV & \aoFgadrmsVI & \aoFgadrmsVII & \aoFgadrmsVIII \tabularnewline

\begin{table*}
\caption{Regressors used in the analysis of the audio-description.}
\begin{tabular}{lll}
\toprule
\textbf{name} & \textbf{count} & \textbf{description} \\
\midrule
body & 66 & trunk of the body or overlaid clothes \\
bpart & 69 & limbs and trousers \\
facehead & 83 & face(parts) or head(parts) \\
furniture & 50 & big inventory of rooms (insides/outsides) \\
geo & 125 & immobile landmarks \\
geo-room & 105 & elements defining a locale's spatial layout \\
setting\_new & 86 & first-time mentioned setting \\
setting\_old & 37 & recurring setting \\
object & 284 & inanimate entities with firm boundaries \\
sex\_f & 108 & female person(s), name \\
sex\_m & 403 & male person(s), name \\
vse\_new & 96 & control for movie cuts; s. table y \\
vse\_old & 90 & control for movie cuts; s. table y \\
vloc\_change & 89 & control for movie cuts; s. table y \\
vpe\_new & 386 & control for movie cuts; s. table y \\
vpe\_old & 208 & control for movie cuts; s. table y \\
fg\_ad\_lrdiff & xx &  left-right volume difference \\
fg\_ad\_rms & xx & root mean square amplitude \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}
\caption{Regressors used in the analysis of the movie.}
\begin{tabular}{lll}
\toprule
\textbf{name} & \textbf{count} & \textbf{description} \\
\midrule
vse\_new & 96 & change of the camera position to a setting not depicted before \\
vse\_old & 90 & change of the camera position to a recurring setting \\
vloc\_change & 89 & change of the camera position to another locale within the same setting \\
vpe\_new & 386 & change of the camera position within a locale not depicted before \\
vpe\_old & 208 & change of the camera position within a recurring locale \\
no\_cut & 148 & a continuous frame from the same camera position \\
se\_new & 148 & audio-description's narrator; s. table x; KANN RAUS? \\
se\_old & 148 & audio-description's narrator; s. table x; KANN RAUS? \\
fg\_av\_ger\_lr & xx & left right +++???+++ in movie frame  \\
fg\_av\_ger\_lrdiff & xx & left-right volume difference \\
fg\_av\_ger\_pd & xx & perceptual differences of consecutive frames \\
fg\_av\_ger\_rms & xx & root mean square amplitude \\
fg\_av\_ger\_ud & xx & +++up down???+++ \\
\bottomrule
\end{tabular}
\end{table*}
% over length of each noun
The regressors were modeled as boxcar functions at the end of each noun with a duration of 200 ms.
If a segment did not contain a single event for a specific regressor, a null regressor was chosen for that segment.
Five regressors related to the cinematographic cuts (s. below) were added to built contrasts of cross-modal negative control.
Two regressors reflecting auditory (low-level) features (left-right loudness volume / amplitude??? difference; root mean squared amplitude) aligned to the frame rate of (40\,ms) were modeled to reduce nuisance effects.
An overview and short explanation of the 11 regressors and 5 + 2 additional nuisance regressors can be found in Table xy.
% entgegen der Masterarbeit kommen hier für den Film keine Abbildungen zur Verdeutlichung, weniger Text; no cut erkläre ich nicht lang & breit
% die regressoren settinge_new & setting_old aus dem Hörspiel habe ich meiner meinung nach unnötigerweise im Film mit-modelliert; lasse mich da aber auch umstimmen

@@
